The effects of linkage disequilibrium on maintaining balanced polymorphisms in seasonal adaptation

### 2019-12-04 writing/manuscript.Rmd
changed figure references

```{r, fig.height = 3, fig.width = 5, fig.cap = 'A density plot of the allele frequencies at the final generation for five replicates of each value of the epistatis parameter. \\label{epi_density}', message = FALSE, echo = FALSE}
setwd(here::here("results/cross_over"))

@@

```{r, fig.height = 3, fig.width = 5, fig.cap = 'A density plot of the allele frequencies at the final generation for five replicates of each number of generations per year. \\label{gen_density}', message = FALSE, echo = FALSE}
setwd(here::here("results/seasonal_balance"))

>>>>

```{r, fig.height = 3, fig.width = 5, fig.cap = 'A density plot of the allele frequencies at the final generation for five replicates of each value of the epistatis parameter. \\label{cross_density}', message = FALSE, echo = FALSE}
setwd(here::here("results/cross_over"))

@@

```{r, fig.height = 3, fig.width = 5, fig.cap = 'A density plot of the allele frequencies at the final generation for five replicates of each number of generations per year. \\label{sb_density}', message = FALSE, echo = FALSE}
setwd(here::here("results/seasonal_balance"))
